|

### 2024-04-17 docs/paper.qmd
Added observational data analyses

---
title: |
  | Accountants' Attitudes Towards Open Science^[Joachim Gassen is based at Humboldt-Universität zu Berlin while Jacqueline Klug and Victor van Pelt are affiliated with WHU Otto Beisheim School of Management. We thank the audience of a workshop at Humboldt University for providing helpful feedback. Excellent research assistance by Benedikt Hahn is gratefully acknowledged. This work was supported by Deutsche Forschungsgemeinschaft (Project-ID 403041268, TRR 266 Accounting for Transparency).]
author: 
  - name: Joachim Gassen
    email: gassen@wiwi.hu-berlin.de
    affiliation: Humboldt-Universität zu Berlin
  - name: Jacqueline Klug
    email: Jacqueline.Klug@whu.edu
    affiliation: WHU Otto Beisheim School of Management
  - name: Victor van Pelt
    email: Victor.vanPelt@whu.edu 
    affiliation: WHU Otto Beisheim School of Management
date: last-modified
date-format: long
execute:
  echo: false
  message: false
  warning: false
format:
  pdf:
    documentclass: article
    number-sections: true
    colorlinks: true
    papersize: letter
    fig-pos: H
    fig_caption: yes
    fig-cap-location: top
    geometry: margin=1in
    fontsize: 11pt
    ident: yes

@@

sd <- readRDS("../data/generated/survey_response.rds")
mr <- readRDS("../data/generated/merged_response.rds")
vars <- read_csv("../data/external/variables.csv", show_col_types = FALSE)
pop <- read_csv("../data/external/invited_authors.csv", show_col_types = FALSE)
```

```{=tex}
\thispagestyle{empty}
\begin{abstract}
\singlespace
Surveying a sample of scholars that have published in leading accounting journals, we document that we accounting researchers are more skeptical about the reproducibility of our influential findings than researchers from other social science areas are about theirs. Also, we are less familiar with public sharing of research materials (data, code, and research procedures) and have less experience with pre-registrating our study designs, two prominent open science measures to increase the reproducibility of research. Our respondents state that they are open to sharing and would be likely to share research materials under a hypothetical scenario, regardless of the experimental framing. They also believe that other accounting researchers, as well as editors, are in favor of research material sharing. However, they are skeptical about the actual prevalence of research material sharing in the accounting research community. In addition, they are more reluctant than researchers from neighboring fields to pre-register their study plans. We interpret this descriptive evidence as indicating an "accounting open science dilemma" and suggest strategies for addressing it.
\end{abstract}
```
\vspace{2cm}

@@

Cumulative science builds on reproducible research.[^1] Across all fields of science [@B_2016; @CDF_2016; @M_2017] and within accounting [@HLL_2000; @G_2023; @S_2023; @CGL_2023], scholars have diagnosed shortcomings in reproducibility and advocated open science methods like public sharing of research materials and the pre-registration of study plans as potential strategies to improve the reproducibility of our work. Prior work across the social sciences [@FLCPSWMBP_2023] has documented an overall uptake of open sciences approaches across several disciplines. We contrast these findings with a survey that we conducted among accounting researchers to explore the perceptions and attitudes toward open science in our field.

[^1]: While in the survey itself, we use the term reproducibility without an exact definition, throughout this article, we follow the notion of @NSF_2015 to define reproducibility as the "ability of a researcher to duplicate the results of a prior study using the same materials and procedures as were used by the original investigator" while replicability "refers to the ability of a researcher to duplicate the results of a prior study if the same procedures are followed but new data are collected". For a more in-depth discussion of the related terminological debate, see @GFI_2016. The key reason why we do not provide an exact definition in the survey is that the differences between reproducibility and replicability are subtle and vary across accounting subfields: For archival studies, reproducibility and replicability should be essentially the same, while for experimental studies they clearly differ.

Based on the responses of `r nrow(sd)` published accounting researchers, we find that our attitudes towards open science clearly differ from those of other researchers in the social sciences. Most prominently, we tend to hold a generally more critical view of the reproducibility of our influential work. Compared to the fields of economics and sociology, for example, we are about half a point more skeptical about the reproducibility of the influential work in our field on a 5-point Likert scale. This is a sizable difference.

Exploring this assessment across our respondents' demographics, we find it to be relatively stable. Analytical and qualitative researchers are somewhat more pessimistic than the other methodologies. Analytical researchers tend to be particularly more critical of research that uses non-analytical methods.

Given this finding, one would expect accounting researchers to take a proactive stand and embrace two prominent open science approaches that methodological work has identified to increase the reproducibility of research: the public sharing of research materials (i.e., data, code and research procedures) and the pre-registration of research plans.

Turning first to the public sharing of research materials, we document that, again compared with researchers from other social science areas, we accounting researchers are somewhat less familiar with this activity. Also, we find it somewhat less important. Familiarity is generally largest for respondents using archival, field, and experimental methods and smallest for respondents using qualitative methods, which also perceive sharing to be less important.

Similar to, albeit even more pronounced than, other social science researchers, there is a stark contrast in our perceived (prescriptive) importance of research material sharing, our stated willingness to share research materials, and our (descriptive) perception about actual sharing behavior. In a hypothetical scenario, the average stated likelihood for sharing research materials by our respondents is relatively high (i.e., 72%), and this likelihood is more or less unaffected by the randomized nature of the rationale (i.e., collaboration or control) and the sharing scope (public or private).[^2] Also, 50% of our respondents state that they at least sometimes publicly share their research materials. In addition, we think that about 44% of us favor publicly sharing research materials, and we assess 61% of the top-six accounting editors to be in favor of publicly sharing research materials.

@@

All this sounds comforting and consistent with a general supportive stand of the accounting community towards public research material sharing. However, when questioned about the actual percentage of us sharing research materials publicly, the number comes down to a much more sobering 28%. This number and the prescriptive/descriptive gap that it reveals differ significantly across methods: Analytical researchers have the narrowest gap (43% of researchers expected to be in favor and 38% expected to actually share) and archival researchers the widest (45% versus 24%). The overall lowest numbers are again reported by qualitative researchers (36% versus 18%).

In light of these numbers, it is a logical next step to explore the main reasons against sharing research materials. Overall, the most commonly stated reasons are the proprietary nature of used data (56% of respondents give this reason), the time that it takes to make materials available (30%) and the fear of being scooped when materials become publicly available (23%). Also, 34% of respondents state there is no need for sharing as their data are already publicly available. Unsurprisingly, the reasons clearly differ across methods. For qualitative researchers, deidentification problems are very prominent (46%) and analytical researchers consider the time that it takes to make materials available far less of a reason than researchers using the other methods (i.e., 9.5% versus 30% overall).

Turning to pre-registration, it seems that we accounting researchers are at least as familiar with the concept as other social science researchers. However, we started using it later (roughly 2 years) and use it less frequently (17% versus 27%). Our trust in pre-registered work is generally comparable with other social scientists but significantly lower than trust levels of researchers in Psychology (the field that reports the highest usage rates of pre-registration). A detailed look into differences among the different methodological fields within accounting also reflects this as we find that experimental researchers use pre-registration most (28%) and express the strongest belief that the practice increases the trustworthiness of research.

Taken together, our findings indicate somewhat of an "accounting open science dilemma": We accounting researchers tend to be skeptical about both, the reproducibility of our work, and the ability of research material sharing and pre-registration to improve it. This results in these tools currently being less established in the accounting domain than in other fields. In addition, the challenges that hinder reproducibility and the potential effectiveness of open science tools vary across methodological paradigms. Qualitative research faces different challenges than archival quantitative work, and its differ again from experimental studies. We conclude by discussing these challenges and providing suggestions on how our diagnosed dilemma might be overcome.

@@

To collect the attitudes of accounting researchers towards open science, we conducted a survey among members of the academic accounting community. The survey has been designed using oTree [@CSW_2016]. To recruit respondents for our survey, we identified authors who published in the "Top 6" accounting journals, i.e., Accounting, Organizations and Society, Contemporary Accounting Research, Journal of Accounting and Economics, Journal of Accounting Research, Review of Accounting Studies, The Accounting Review, over the period 2016 to 2021. We chose these six accounting journals because they are commonly known to be top accounting journals within the academic accounting community. We realize that this is not an exhaustive list and that there are divergent views about journals within the accounting community. Yet, we believe that, taken together, these journals provide us with a somewhat representative list of publishing accounting academics. We started compiling the list of authors from 2016 onward because this is the year that Open Science and, more specifically, the reproducibility of research became a more widespread topic of debate among academics within the social sciences and, presumably, accounting researchers [@OSC_2015; @B_2016; @CDF_2016; @M_2017]. After receiving approval from an ethical review board, also guaranteeing the anonymity of the participating respondents, we sent out initial invitations and a total three reminders. We allowed potential respondents to opt out of future emails every time we reached out to them. Please see Appendix A for the invitation emails.

@@

Table 1 displays our sample selection procedures. Of the 2,660 potential respondents we approached, we excluded 118 for various reasons.[^3] Furthermore, for 206 emails bounced, we received a notification that the email address was unreachable. Of the remaining 2,336 successfully reached accounting researchers, 391 started the study (15,4% of the total emails sent), 254 partially completed the study (10,9% of the total emails sent), and 222 fully completed the study (8,7% of the total emails sent).[^4] Table 2 displays our final sample's demographics and characteristics. Panel A reveals that the majority of the respondents is male, 35 years or older (87.8%), specializes in Financial Accounting and Reporting or Managerial Accounting (70.3%), has Archival or Field Research as their primary research method (55.9%), and is from North America or Europe (91%).

[^3]: 41 authors were removed because we found no email address, 41 authors were removed because they appeared in the data twice with two author IDs but were the same person, 28 authors were removed because they were a current member of one of our affiliated universities or academic research centers, 5 authors were removed because they gave us advice for this study, 2 authors were removed because they had passed away, and 1 author was removed due to an incorrect email address.

[^4]: As the dependent variable of our hypothetical scenario analysis outlined below is the first data that we collect, 254 is the sample size for this analysis. For the descriptive analyses, we settle for the number of participants that answered the respective question and, if applicable, also provided the necessary demographics for cross-sectional splits. Depending on this, the sample sizes vary from 222 to 229 responses. 
\centerline{--- Insert Table 2 about here ---}

Panel B of Table 2 contrasts our respondent sample with our sampling population. Given the anonymity of our response and the data that we are able to collect about our population we are only able to compare the geographic dispersion of our sample. Panel B reveals that, in particular, researchers from Europe are over-represented and researchers from Asia are under-represented in the sample. Given that response rate assessment is inherently hard, we generally abstain from speculating about potential reasons for this sampling imbalance. However, it seems likely that the all-European author team of the study might have had an influence. While we control for geographical effects in our response (not-tabulated) and find only mild variation across regions (researchers from North America tend to state higher sharing activities and preferences), we conclude from this sampling imbalance that our results mostly speak to the attitudes of accounting scholars from North America and Europe and that we can say very little about researchers located in Asia that happen to have a very low response rate.

@@

To ensure that our findings are comparable with related prior work, we adapted key questions from the Survey of Open Science Practices and Attitudes in the Social Sciences [@FLCPSWMBP_2023], which has been recently published in Nature Communications. Very similar to our survey, this study solicits the view by published researchers and PhD students on reproducibilty, research material sharing, and pre-registration. Given that it differs in survey detail (app. 45 minutes while our survey was designed to be completed in less than 10 minutes), and data collection procedure (confidential with compensation element while we use an anonymous survey with very mild incentivization), we had to make some adjustments. However, the ordering and phrasing of questions in our survey are similar and their content and answer scales are identical or differ in a negligible way. Specifically, we decided to alter the framing and expand some of the questions to make it easier for accounting researchers to understand the questions and connect them to their common research practices. We also pre-tested our adapted questions among a group of doctoral students specializing in accounting, which indicated no issues with the adapted questions.

The first stage of the survey included questions about respondents' views on publicly sharing research materials, which we described as comprising of data, code, and research procedures. Specifically, we asked respondents about their familiarity with public sharing of research materials and their views of its importance. We also asked them about their perceptions of the prevalence of sharing in the accounting research community, how often they tended to share, and whether they planned to share in the future. Conditional on whether respondents indicated that they do not always share, we also asked them for the reasons behind not sharing. Lastly, we asked respondents to estimate what percentage of accounting researchers favor sharing and their approximation of the percentage of editors of the top six accounting journals that believe sharing increases the value of a manuscript.

The second stage of the survey featured a selection of questions about respondents' views on reproducibility and pre-registration, which we also borrowed and adapted from @FLCPSWMBP_2023 . First, we asked respondents about their confidence in the reproducibility of accounting research. We also asked them about their subfield within the domain of accounting (i.e., Auditing, Financial Accounting and Reporting, Managerial Accounting, Taxation, Accounting information systems, and Other) and whether they believe the findings in their field are reproducible. Next, we asked the same questions for their methodological area (i.e., Analytical, Archival/Field, Experimental, Qualitative, Survey, and Other). Subsequently, we asked respondents about their familiarity and experience with the practice of pre-registration. Lastly, we asked them about their perceptions of trustworthiness of pre-registered research compared to non-pre-registered research. We completed the survey with asking a few demographic questions that are mostly presented in Table 2. For a complete overview of the survey questions included in our study, please see Appendix A.

@@

The first goal of the survey was to gauge the perceptions of accounting researchers regarding the reproducibility of influential findings in the accounting literature. Table 3 displays a detailed overview of our respondents' answers to the question "How confident are you that the influential findings in the area of accounting overall are reproducible?" The table also contrasts the answers provided by our respondents with the answers submitted by researchers in other fields in the survey conducted by @FLCPSWMBP_2023 , who asked the question "How confident are you that the influential research findings in \[discipline\] would replicate?" We changed the wording from "replicating" to "reproducing" in our adapted question to make it more recognizable to a diverse group of researchers, such as those in the academic accounting community. Namely, the term "reproducibility" is a focal point in the discussion across the social sciences, including accounting [@B_2016; @CDF_2016; @M_2017; @HLL_2000]. In contrast, the term"replication" may or may not have different interpretations for different researchers. For instance, experimental researchers it refers to distinct activity (i.e., repeating an experimental study), while for archival researchers, it refers to a similar activity (i.e., re-analyzing the same data using the same procedures).

@@

Figure 1 visually represents the data from Table 3 by plotting them on a horizontal axis and aligning them around a neutral midpoint. The figure shows that accounting researchers are the most skeptical (i.e., "Not at all confident") about the reproducibility of influential findings in their field (10.5%). This difference is much higher than the percentage of skeptics reported by @FLCPSWMBP_2023: 0.7% for Economics, 2.1% for Political Science, and 1.1% for Psychology, and 1.3% for Sociology. The field of Accounting, therefore, also has the lowest percentage of non-skeptics (i.e., researchers who are either moderately or extremely confident in the reproducibility of influential findings). That is, Accounting has about 39.3% non-skeptics, while Economics has 61.1%, Political Science has 45.8%, Psychology has 41.3%, and Sociology has 61.7%. The differences with Economics and Sociology again are the largest, while the differences with Political Science and Psychology are smaller.

Next, we compare assessments of accounting researchers regarding reproducibility across different methodologies. Accounting is not only a diverse discipline in terms of orientation and topic, but also in terms of the methodologies its researchers employ. We distinguish among five categories: Analytical, Archival/Field, Experimental, Qualitative, and Survey. We asked respondents which of those categories best described their main methodological area, enabling us to categorize them in the data. Table 4 displays their assessments regarding the reproducibility of influential findings across three panels. Panel A focuses on assessments of reproducibility within accounting as a whole, Panel B on assessments within their main methodological area, and Panel C on differences in assessments between accounting as a whole and their main methodological area.

@@

The findings in Table 4 Panel A suggest that analytical and qualitative researchers are more pessimistic and skeptical about the reproducibility of influential findings in accounting as whole than accounting researchers using other methodologies. In particular, analytical researchers are significantly less confident about the reproducibility of influential findings in accounting in general than researchers in the Archival/Field and Experimental categories (two-tailed p-value \< 0.100). When turning to respondents' assessments of the reproducibility of influential findings in their own methodological area, we find that analytical researchers have the most confidence in the influential findings within their methodological area as their average confidence is statistically higher from those reported by the average reported for the other four methodologies (two-tailed p-value \< 0.100). Qualitative research reports a significantly lower average confidence than Analytical, Archival/Field, and Experimental research, albeit it is indistinguishable from the average confidence reported by those in the Survey category (two-tailed p-value \> 0.100).

Panel C reports the "assessment gap," which captures the difference in assessments of the reproducibility of influential findings in respondents' own methodological area versus accounting in general. A higher (lower) assessment gap indicates that respondents are more (less) confident in the reproducibility of influential findings in their methodological area compared to accounting in general. The findings of Panel C report that analytical researchers report the largest assessment gap, implying they are relatively skeptical about reproducibility of influential findings in accounting as a whole compared to their own methodology. The average assessment gap reported for the Analytical category is also statistically different from the averages reported in the other four categories (two-tailed p-value \< 0.100). The other four categories exhibit no clear assessment gap (with averages hovering around zero) and are statistically indistinguishable form each other.

@@

Accounting researchers so far show a disproportionate skepticism toward the reproducibility in their field and with some variation across methodologies. Given the skepticism,we have observed so far, one would expect accounting researchers to take a more proactive stance on open science approaches, like the practice of research materials sharing. The survey assessed respondents' evaluations of the practice of research materials sharing next. Specifically, we asked respondents two questions about the practice of sharing research materials, which we defined as the practice of sharing data, code, and research procedures. These two questions were also close adaptions of the survey done by @FLCPSWMBP_2023.

@@

### Sharing Research Materials - Prescriptive versus Descriptive Views and Rationales

>>>>

---
title: |
  | Accountants' Attitudes Towards Open Science^[Joachim Gassen is based at Humboldt-Universität zu Berlin while Jacqueline Klug and Victor van Pelt are affiliated with WHU Otto Beisheim School of Management. We thank Kris Hardies and  audiences of workshops at University of Antwerp and Humboldt University Berlin for providing helpful feedback. Excellent research assistance by Benedikt Hahn, Fabian Kalife, and Timnah Weckner is gratefully acknowledged. This work was supported by Deutsche Forschungsgemeinschaft (Project-ID 403041268, TRR 266 Accounting for Transparency).]
author: 
  - name: Joachim Gassen
    email: gassen@wiwi.hu-berlin.de
    affiliation: Humboldt-Universität zu Berlin
  - name: Jacqueline Klug
    email: Jacqueline.Klug@whu.edu
    affiliation: WHU Otto Beisheim School of Management
  - name: Victor van Pelt
    email: Victor.vanPelt@whu.edu 
    affiliation: WHU Otto Beisheim School of Management
date: last-modified
date-format: long
execute:
  echo: false
  message: false
  warning: false
format:
  pdf:
    documentclass: article
    number-sections: true
    colorlinks: true
    papersize: letter
    fig-pos: H
    fig_caption: yes
    fig-cap-location: top
    geometry: margin=1in
    fontsize: 11pt
    ident: yes

@@

sd <- readRDS("../data/generated/survey_response.rds")
mr <- readRDS("../data/generated/merged_response.rds")
vars <- read_csv("../data/external/variables.csv", show_col_types = FALSE)
pop <- read_csv("../data/external/invited_authors_anon.csv", show_col_types = FALSE)

authors <- read_csv("../data/external/obs_data_authors_anon.csv", show_col_types = FALSE)
papers <- read_csv("../data/external/obs_data_papers_anon.csv", show_col_types = FALSE)

source("../code/obs_data_analyses.R")
```

```{=tex}
\thispagestyle{empty}
\begin{abstract}
\singlespace
Surveying a sample of scholars that have published in leading accounting journals, we document that we accounting researchers are more skeptical about the reproducibility of our influential findings than researchers from other social science areas are about theirs. Also, we are less familiar with the public sharing of research materials (data, code, and research procedures) and have less experience with pre-registrating our study designs, two prominent open science measures to increase the reproducibility of research. Our respondents state that they are open to sharing and would likely share research materials under a hypothetical scenario, regardless of provided rationale and scope. They also believe that other accounting researchers, as well as editors, are in favor of research material sharing. However, they are skeptical about the actual prevalence of research material sharing in the accounting research community. In addition, they are more reluctant than researchers from neighboring fields to pre-register their study plans. We interpret this descriptive evidence as indicating an "accounting open science dilemma" and suggest strategies for addressing it.
\end{abstract}
```
\vspace{2cm}

@@

Cumulative science builds on reproducible research.[^1] Across all fields of science [@B_2016; @CDF_2016; @M_2017] and within accounting [@HLL_2000; @G_2023; @S_2023; @CGL_2023], scholars have diagnosed shortcomings in reproducibility and advocated open science methods like public sharing of research materials and the pre-registration of study plans as potential strategies to improve the reproducibility of our work. Prior work across the social sciences has documented an overall uptake of open sciences approaches across several disciplines [@FLCPSWMBP_2023]. We contrast these findings with a survey that we conducted among accounting researchers to explore the perceptions and attitudes toward open science in our field.

[^1]: While in the survey itself, we use the term reproducibility without an exact definition, throughout this article, we follow the notion of @NSF_2015 to define reproducibility as the "ability of a researcher to duplicate the results of a prior study using the same materials and procedures as were used by the original investigator" while replicability "refers to the ability of a researcher to duplicate the results of a prior study if the same procedures are followed but new data are collected". For a more in-depth discussion of the related terminological debate, see @GFI_2016. The key reason why we do not provide an exact definition in the survey is that the differences between reproducibility and replicability are subtle and vary across accounting subfields. For archival studies, reproducibility and replicability should be essentially the same, while for experimental studies they clearly differ.

Based on the responses of `r nrow(sd)` published accounting researchers, we find that our attitudes towards open science clearly differ from those of other researchers in the social sciences. Most prominently, we tend to hold a generally more critical view of the reproducibility of our influential work. Compared to the fields of economics and sociology, for example, we are about half a point more skeptical about the reproducibility of the influential work in our field on a 5-point Likert scale. Exploring this assessment across our respondents' demographics, we find this skepticism to be relatively stable. Analytical and qualitative researchers are somewhat more pessimistic than the other methodologies. Analytical researchers tend to be particularly more critical of research that uses non-analytical methods.

Given this finding, one would expect accounting researchers to take a more proactive stance and embrace two prominent open science approaches that methodological work has identified to increase the reproducibility of research: The public sharing of research materials (i.e., data, code and research procedures) and the pre-registration of research plans. Turning first to the public sharing of research materials, we document that, again, compared to researchers from other social science areas, we accounting researchers are somewhat less familiar with this activity. Also, we find it somewhat less important. Familiarity is generally largest for respondents using archival, field, and experimental methods and smallest for respondents using qualitative methods, which also perceive sharing as less important.

Similar to, albeit even more pronounced than, other social science researchers, there is a stark contrast in our perceived (prescriptive) importance of research material sharing, our stated willingness to share research materials, and our (descriptive) perception about actual sharing behavior. In a hypothetical scenario, the average stated likelihood for sharing research materials by our respondents is relatively high (i.e., 72%), and this likelihood is more or less unaffected by the randomized nature of the provided rationale (i.e., collaboration or control) and the provided scope (public versus private sharing).[^2] Also, 50% of our respondents state that they, at least sometimes, publicly share their research materials. In addition, our respondents believe that about 44% of us favor publicly sharing research materials, and they believe 61% of the top-six accounting editors to be in favor of publicly sharing research materials.

@@

All this sounds comforting and consistent with a general supportive stand of the accounting community towards public research material sharing. However, when asked about respondents' perceptions about actual sharing behavior, the percentage comes down to a much more sobering 28%. This sober number and the gap it reveals differ significantly across the different accounting methodological areas. Analytical researchers have the narrowest gap (they expect 43% of accounting researchers to be in favor and 38% to actually share research materials). Archival researchers, in turn, have the widest gap (45% expected to be in favor versus 24% expected to actually share). The overall lowest numbers are again reported by qualitative researchers (36% versus 18%).

Using observational data from a country-stratified random sample of `r nrow(authors)` authors from our target population to contrast these perceptions with actual behavior, we find at least some evidence for research material sharing for 39 % of this random sample. This number is largely in line with the self-reported figures but masks that research material sharing in accounting seems to be largely an occasional compliance activity: Only for 7.5 % of the papers that we analyze we find evidence for research material sharing and when we exclude Journal of Accounting Research and Management Science, two journals with data and code policies in place, the share of authors for which we document research material sharing evidence drops from 39 to 23 %.

In light of these numbers, it is a logical next step to explore the main reasons against sharing research materials. Overall, the most commonly stated reasons for not sharing research materials are the proprietary nature of the used data (56% of respondents give this reason), the time it takes to make materials available (30%), and the fear of being scooped when materials become publicly available (23%). Additionally, 34% of respondents state that there is no need for sharing as their data is already publicly available. Unsurprisingly, the reasons clearly differ across methods. For qualitative researchers, deidentification problems are very prominent (46%), and analytical researchers consider the time it takes to make materials available far less of a reason than researchers using other methods (i.e., 9.5% versus 30% overall).

Regarding pre-registration, it seems that we accounting researchers are at least as familiar with the concept as other social science researchers. However, our respondents report that they started using it later than other social science researchers (roughly two years) and that they use it less frequently (17% versus 27%). Our trust in pre-registered work is generally comparable with other social scientists but significantly lower than the trust levels of researchers in Psychology (the field that reports the highest usage rates of pre-registration). A detailed look into differences among the different methodological fields within accounting also reflects this, as we find that experimental researchers use pre-registration the most (28%) and express the strongest belief that the practice increases the trustworthiness of research.

Taken together, our findings indicate somewhat of an "accounting open science dilemma": We accounting researchers tend to be skeptical about both the reproducibility of our work, and the ability of research material sharing and pre-registration to improve it. This results in these tools currently being less established in the accounting domain than in other fields. In addition, the challenges that hinder reproducibility and the potential effectiveness of open science tools vary across methodological paradigms. Qualitative research faces different challenges than archival quantitative work, and they both differ again from experimental studies. We conclude by discussing these challenges and providing suggestions on how our diagnosed dilemma might be overcome.

@@

To collect the attitudes of accounting researchers towards open science, we conducted a survey among members of the academic accounting community. The survey has been designed using oTree [@CSW_2016]. To recruit respondents for our survey, we identified authors who published in the "Top 6" accounting journals, i.e., Accounting, Organizations and Society, Contemporary Accounting Research, Journal of Accounting and Economics, Journal of Accounting Research, Review of Accounting Studies, The Accounting Review, over the period 2016 to 2021. We chose these six accounting journals because they are commonly known to be top accounting journals within the academic accounting community. We realize that this is not an exhaustive list and that there are divergent views about journals within the accounting community. Yet, we believe that, taken together, these journals provide us with a representative list of publishing accounting academics. We started compiling the list of authors from 2016 because this is the year that Open Science and, more specifically, the reproducibility of research became a more widespread topic of debate among academics within the social sciences and, presumably, accounting researchers [@OSC_2015; @B_2016; @CDF_2016; @M_2017]. After receiving approval from an ethical review board, also guaranteeing the anonymity of the participating respondents, we sent out initial invitations and a total of three reminders. We allowed potential respondents to opt out of future emails every time we reached out to them. Please see Appendix A for the invitation emails.

@@

Table 1 displays our sample selection procedures. Of the 2,660 potential respondents we identified, we excluded 118 for various reasons.[^3] Furthermore, for 206 emails bounced, we received a notification that the email address was unreachable. Of the remaining 2,336 successfully reached accounting researchers, 391 started the study (15,4% of the total emails sent), 254 partially completed the study (10,9% of the total emails sent), and 222 fully completed the study (8,7% of the total emails sent).[^4] Table 2 displays our final sample's demographics and characteristics. Panel A reveals that the majority of the respondents are male, 35 years or older (87.8%), specialize in Financial Accounting and Reporting or Managerial Accounting (70.3%), has Archival or Field Research as their primary research method (55.9%), and is from North America or Europe (91%).

\centerline{--- Insert Table 2 about here ---}

[^3]: We removed 41 authors because we found no email address, 41 authors because they appeared in the data twice with two author IDs but were the same person, 28 authors because they were a current member of one of our affiliated universities or academic research centers, 5 authors because they gave us advice for this study, 2 authors because they had passed away, and 1 author due to an incorrect email address.

[^4]: As the dependent variable of our hypothetical scenario analysis outlined below is the first data we collect, 254 is the sample size for this analysis. For the descriptive analyses, we settle for the number of participants that answered the respective question and, if applicable, also provided the necessary demographics for cross-sectional splits. Depending on this, the sample sizes for the descriptive analyses vary from 222 to 229 responses.

Panel B of Table 2 contrasts our respondent sample with our sampling population. Given the anonymity of our response and the data that we can collect about our population, we can only compare the geographic dispersion of our sample. Panel B reveals that, in particular, researchers from North America and Europe are over-represented, and researchers from Asia are under-represented in the sample. Given that response rate assessment is inherently challenging, we generally avoid speculating about potential reasons for this sampling imbalance. However, it seems likely that the study's all-European author team might have positively influenced the European response. While we control for geographical effects in our response (not-tabulated) and find only mild variation across regions (researchers from North America tend to state higher sharing activities and preferences), we conclude from this sampling imbalance that our results mostly speak to the attitudes of accounting scholars from North America and Europe and that we can say very little about researchers located in Asia and other geographical regions that happen to have low response rates.

@@

To ensure that our findings are comparable with related prior work, we adapted key questions from the Survey of Open Science Practices and Attitudes in the Social Sciences [@FLCPSWMBP_2023], which has been recently published in Nature Communications. Similar to our survey, this study solicits the views of published researchers and PhD students on reproducibility, research material sharing, and pre-registration. Given that it differs in depth (approximately 45 minutes while our survey was designed to be completed in less than 10 minutes) and data collection procedure (confidential with compensation element while we use an anonymous survey with mild incentivization), we had to make some adjustments. However, the ordering and phrasing of questions in our survey are similar, and their content and answer scales are identical or differ in a negligible way. Specifically, we decided to alter the framing and expand some of the questions to make it easier for accounting researchers to understand the questions and connect them to their commonly accepted research practices. We also pre-tested our adapted questions among a group of doctoral students specializing in accounting, which indicated no issues with the adapted questions.

The first stage of the survey included questions about respondents' views on publicly sharing research materials, which we described as comprising data, code, and research procedures. Specifically, we asked respondents about their familiarity with the public sharing of research materials and their views of their importance. We also asked them about their perceptions of the prevalence of sharing in the accounting research community, how often they tended to share, and whether they planned to share in the future. Conditional on whether respondents indicated that they do not always share, we also asked them for the reasons behind not sharing. Lastly, we asked respondents to estimate what percentage of accounting researchers favor sharing and their approximation of the percentage of editors of the top six accounting journals that believe sharing increases the value of a manuscript.

The second stage of the survey featured a selection of questions about respondents' views on reproducibility and pre-registration, which we also borrowed and adapted from @FLCPSWMBP_2023 . First, we asked respondents about their confidence in the reproducibility of accounting research. We also asked them about their subfield within the domain of accounting (i.e., Auditing, Financial Accounting and Reporting, Managerial Accounting, Taxation, Accounting information systems, and Other) and whether they believe the findings in their field are reproducible. Next, we asked the same questions for their methodological area (i.e., Analytical, Archival/Field, Experimental, Qualitative, Survey, and Other). Subsequently, we asked respondents about their familiarity and experience with the practice of pre-registration. Lastly, we asked them about their perceptions of the trustworthiness of pre-registered research compared to non-pre-registered research. We completed the survey by asking a few demographic questions that are primarily presented in Table 2. For a complete overview of the survey questions included in our study, please see Appendix A.

@@

The first goal of the survey was to gauge the perceptions of accounting researchers regarding the reproducibility of influential findings in the accounting literature. Table 3 displays a detailed overview of our respondents' answers to the question, "How confident are you that the influential findings in the area of accounting overall are reproducible?" The table also contrasts the answers provided by our respondents with the answers submitted by researchers in other fields in the survey conducted by @FLCPSWMBP_2023 , who asked the question "How confident are you that the influential research findings in \[discipline\] would replicate?" We changed the wording from "replicating" to "reproducing" in our adapted question to make it more recognizable to a diverse group of researchers, such as those in the academic accounting community. Namely, the term "reproducibility" is a focal point in the discussion across the social sciences, including accounting [@B_2016; @CDF_2016; @M_2017; @HLL_2000]. In contrast, the term"replication" may or may not have different interpretations for different researchers. For instance, experimental researchers it refers to a distinct activity (i.e., repeating an experimental study), while for archival researchers, it refers to a similar activity (i.e., re-analyzing the same data using the same procedures).

@@

Figure 1 visually represents the data from Table 3 by plotting them on a horizontal axis and aligning them around a neutral midpoint. The figure shows that accounting researchers are the most skeptical (i.e., "Not at all confident") about the reproducibility of influential findings in their field (10.5%). This difference is much higher than the percentage of skeptics reported by @FLCPSWMBP_2023: 0.7% for Economics, 2.1% for Political Science, and 1.1% for Psychology, and 1.3% for Sociology. The field of Accounting, therefore, also has the lowest percentage of non-skeptics (i.e., researchers who are either moderately or extremely confident in the reproducibility of influential findings). That is, Accounting has about 39.3% non-skeptics, while Economics has 61.1%, Political Science has 45.8%, Psychology has 41.3%, and Sociology has 61.7%. The differences with Economics and Sociology again are the largest, while the differences between Political Science and Psychology are smaller.

Next, we compare assessments of accounting researchers regarding reproducibility across different methodologies. Accounting is not only a diverse discipline in terms of orientation and topic but also in terms of the methodologies its researchers employ. We distinguish among five categories: Analytical, Archival/Field, Experimental, Qualitative, and Survey. We asked respondents which of those categories best described their main methodological area, enabling us to categorize them in the data. Table 4 displays their assessments regarding the reproducibility of influential findings across three panels. Panel A focuses on assessments of reproducibility within accounting as a whole, Panel B on assessments within their main methodological area, and Panel C on differences in assessments between accounting as a whole and their main methodological area.

@@

The findings in Table 4 Panel A suggest that analytical and qualitative researchers are more pessimistic and skeptical about the reproducibility of influential findings in accounting as a whole than accounting researchers using other methodologies. In particular, analytical researchers are significantly less confident about the reproducibility of influential findings in accounting in general than researchers in the Archival/Field and Experimental categories (two-tailed p-value \< 0.100). When turning to respondents' assessments of the reproducibility of influential findings in their own methodological area, we find that analytical researchers have the most confidence in the influential findings within their methodological area as their average confidence is statistically higher from those reported by the average reported for the other four methodologies (two-tailed p-value \< 0.100). Qualitative research reports a significantly lower average confidence than Analytical, Archival/Field, and Experimental Research, albeit it is indistinguishable from the average confidence reported by those in the Survey category (two-tailed p-value \> 0.100).

Panel C reports the "assessment gap," which captures the difference in assessments of the reproducibility of influential findings in respondents' own methodological area versus accounting in general. A higher (lower) assessment gap indicates that respondents are more (less) confident in the reproducibility of influential findings in their methodological area compared to accounting in general. The findings of Panel C report that analytical researchers report the largest assessment gap, implying they are relatively skeptical about the reproducibility of influential findings in accounting as a whole compared to their own methodology. The average assessment gap reported for the Analytical category is also statistically different from the averages reported in the other four categories (two-tailed p-value \< 0.100). The other four categories exhibit no clear assessment gap (with averages hovering around zero) and are statistically indistinguishable from each other.

@@

Accounting researchers so far show a disproportionate skepticism toward the reproducibility in their field and with some variation across methodologies. Given the skepticism, we have observed so far, one would expect accounting researchers to take a more proactive stance on open science approaches, like the practice of research materials sharing. The survey assessed respondents' evaluations of the practice of research materials sharing next. Specifically, we asked respondents two questions about the practice of sharing research materials, which we defined as the practice of sharing data, code, and research procedures. These two questions were also close adaptions of the survey done by @FLCPSWMBP_2023.

@@

### Sharing Research Materials - Prescriptive versus Descriptive Views
